### 2019-08-14 README.Rmd
updated to do list after meeting yesterday

@@

- work on first draft of paper
- read through papers giving an overview of the current explanation methods

>>>>

- Graphics Group
    - email list (should I be added as an admin?)

@@

- keep the LIME procedure at a higher level in the paper
- check for ridge regression model in Python code
- compute generalized $R^2$ for my images
- change to computing the $\mathcal{L}$ metric from the paper
- check if Python package outputs the locality metric
- add figure descriptions in both caption and text
- move sentence on various settings to back of paper
- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- get rid of current implementation in text (change to original paper and mention doing this for model agnostic reasons)
- add an assert_that statement in the code to check if the LIME package is changing
- first draft of paper due two weeks into the semester (September 10)
- read through papers giving an overview of the current explanation methods
